Tables in the project

### 2018-08-03 paper/Chapters/Chapter2.tex
tables figs of MLCA done, classes and bmi, dm, hyt estimates needed

The number of classes in either level 1 were determined by 1) the evaluation of model fit indices, including the Akaike information criterion (AIC), Bayesian information criterion (BIC), adjusted Bayesian information criterion (aBIC) where smaller values indicate better, and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compare $q$ vs. $q-1$ class models, where $q$ is the number of latent classes and 3) pattern interpretability. In the step of performing multilevel LCA, where LMR-LRT is available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in observation day level and individual level. MLCA models were fitted in Mplus 7.4 \parencite{muthen2005mplus}, the Mplus codes are shown in \textbf{Appendix \ref{AppendixB}}. \vspace{-0.3cm}

@@

\section{Day level latent classes and their characteristics}\vspace{-0.3cm}

Day level latent classes identified by MLCA steps were tabulated according to whether the diary was recorded during weekdays or not. A contingency table giving the frequency of responses across the 7 time slots of the survey days was produced.

>>>>

The number of classes in either level 1 were determined by 1) the evaluation of model fit indices, including the Akaike information criterion (AIC), Bayesian information criterion (BIC), adjusted Bayesian information criterion (aBIC) where smaller values indicate better, and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compare $q$ vs. $q-1$ class models, where $q$ is the number of latent classes and 3) pattern interpretability. In the step of performing multilevel LCA, where LMR-LRT is available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in observation day level and individual level. MLCA models were fitted in Mplus 7.4 \parencite{muthen2005mplus}, the Mplus codes and outputs are shown in \textbf{Appendix \ref{AppendixB}}. \vspace{-0.3cm}

@@

\section{Characteristics of dietary diary and population}\vspace{-0.3cm}

Day level latent classes identified by MLCA steps were tabulated according to whether the diary was recorded during weekdays or not. A contingency table giving the frequency of responses across the 7 time slots of the survey days was produced. Descriptive statistics for the dietary day level recordings according to the latent classes were presented.

\section{Association between individual level latent classes and the prevalence of hypertension, obesity, and diabetes}

### 2018-08-03 paper/Chapters/Chapter3.tex
tables figs of MLCA done, classes and bmi, dm, hyt estimates needed

With two individual level latent classes \textbf{(Figure \ref{fig:CB2level2})}, one individual class is comprised of individuals with a relatively slightly higher proportion of having "low carbohydrate day" (22.1\%) compared to the other (17.4\%). This class represents nearly 65\% of the individuals.

@@

With three individual level latent classes \textbf{(Figure \ref{fig:level2})}, a low-carbohydrate eaters class, moderate-carbohydrate eaters class, and high-carbohydrate eaters class emerges. 43.1\% participants were identified as high-carbohydrate eaters, in these individuals, about 50\% of the days (2 out of 4 days) of their dietary diary were classified as having high carbohydrate days. Nearly 1 out of 4 days of their dietary diary were either "regular meals day" or "low carbohydrate day".

@@

@@

\caption{\label{tab:Level2tab1}Weighted means, percentages, and
95\% CIs of the social, economical characteristics by latent class memberships in the UK
adults. (NDNS RP 2008/09-2015/16, sample size = 6155)} \centering
\fontsize{9}{11}\selectfont

\begin{tabular}[t]{lcccc}
	\hiderowcolors
	\toprule
	\textbf{Variables} & \textbf{\Centerstack{Individual class 1\\(n = 1730)}} & \textbf{\Centerstack{Individual class 2\\(n = 1772)}} & \textbf{\Centerstack{Individual class 3\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\
	\midrule
	\showrowcolors
	Total (\%) & 28.4 (26.9, 29.9) & 28.7 (27.1, 30.3) & 43.0 (41.3, 44.7) & \\
	Countries (\%) &  &  &  & 0.007\\
	\hspace{1em}England & 84.5 (81.7, 86.9) & 82.0 (79.3, 84.5) & 84.7 (82.3, 86.8) & \\
	\hspace{1em}Northern Ireland & 2.1 (1.6, 2.8) & 4.2 (3.2, 5.6) & 2.2 (1.7, 3.0) & \\
	\hspace{1em}Scotland & 9.1 (7.0, 11.8) & 8.6 (6.7, 11.1) & 8.0 (6.3, 10.2) & \\
	\hspace{1em}Wales & 4.3 (3.3, 5.6) & 5.1 (4.0, 6.4) & 5.1 (4.0, 6.4) & \\
	Age (years) & 51.0 (49.9, 52.1) & 40.3 (39.1, 41.6) & 51.7 (50.7, 52.7) & < 0.001\\
	Sex (\%) &  &  &  & 0.119\\
	\hspace{1em}Men & 50.0 (46.9, 53.1) & 50.2 (47.0, 53.5) & 46.6 (44.0, 49.1) & \\
	\hspace{1em}Women & 50.0 (46.9, 53.1) & 49.8 (46.5, 53.0) & 53.4 (50.9, 56.0) & \\
	Survey years (\% in rows) &  &  &  & 0.015\\
	\hspace{1em}1 & 32.5 (28.4, 36.9) & 26.3 (21.9, 31.2) & 41.2 (36.6, 46.0) & \\
	\hspace{1em}2 & 26.8 (22.6, 31.3) & 22.6 (18.6, 27.3) & 50.6 (45.8, 55.4) & \\
	\hspace{1em}3 & 22.6 (18.8, 26.9) & 33.7 (28.6, 39.2) & 43.6 (38.7, 48.7) & \\
	\hspace{1em}4 & 27.9 (24.1, 32.2) & 27.6 (23.8, 31.8) & 44.4 (40.2, 48.7) & \\
	\hspace{1em}5 & 27.9 (24.2, 32.0) & 28.7 (24.4, 33.5) & 43.3 (38.2, 48.6) & \\
	\hspace{1em}6 & 28.0 (24.0, 32.4) & 31.5 (26.9, 36.6) & 40.5 (35.8, 45.3) & \\
	\hspace{1em}7 & 29.1 (25.2, 33.4) & 29.0 (24.5, 34.0) & 41.8 (37.1, 46.7) & \\
	\hspace{1em}8 & 31.1 (27.3, 35.3) & 30.5 (25.9, 35.5) & 38.4 (34.1, 42.8) & \\
	Paid employment\textsuperscript{\dag} (\%) &  &  &  & 0.907\\
	\hspace{1em}Yes & 40.3 (37.0, 43.6) & 40.8 (37.1, 44.5) & 39.8 (37.1, 42.6) & \\
	\hspace{1em}No & 59.7 (56.4, 63.0) & 59.2 (55.5, 62.9) & 60.2 (57.4, 62.9) & \\
	Live with partner\textsuperscript{\ddag} (\%) &  &  &  & < 0.001\\
	\hspace{1em}Yes & 56.9 (53.6, 60.1) & 38.4 (35.2, 41.8) & 61.3 (58.7, 63.7) & \\
	\hspace{1em}No & 43.1 (39.9, 46.4) & 61.6 (58.2, 64.8)) & 38.7 (36.3, 41,3) & \\
	Household Income, \textsterling/year & \Centerstack{36558.53\\(34800.21, 38316.84)} & \Centerstack{27180.80\\(25597.95, 28763.65)} & \Centerstack{32171.58\\(31024.96, 33318.2)} & < 0.001\\
	Ethnicity (\%) &  &  &  & \\
	\hspace{1em}White & 94.2 (92.4, 95.6) & 79.5 (76.4, 82.3) & 91.9 (90.1, 93.4) & < 0.001\\
	\hspace{1em}Non-White & 5.8 (4.4, 7.6) & 20.5 (17.7, 23.6) & 8.1 (6.6, 9.9) & \\
	Education (\%) &  &  &  & \\
	\hspace{1em}Degree or higher & 29.0 (26.1, 32.1) & 23.3 (20.5, 26.3) & 26.2 (24.1, 28.5) & 0.019\\
	\hspace{1em}Lower than degree & 71.0 (67.9, 73.9) & 76.7 (73.7, 79.5) & 73.8 (71.5, 75.9) & \\
	\bottomrule
	\multicolumn{5}{l}{\textit{Note: }}\\
	\multicolumn{5}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme.}\\
	\multicolumn{5}{l}{Variables were weighted by individual weights.}\\
	\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the \textit{F} test was used to determine differences between latent classes with}\\ 
	\multicolumn{5}{l}{Bonferroni correction to account for multiple testing across $>$ 2 classes. For categorical variables,}\\
	\multicolumn{5}{l}{ differences between latent classes were assessed using the adjusted Pearson $\chi^2$ test for survey data.} \\
	\multicolumn{5}{l}{\textsuperscript{\dag} Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey.}\\
	\multicolumn{5}{l}{\textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil} \\
	\multicolumn{5}{l}{partnership.}\\
\end{tabular}

@@

		\textbf{Variables} & \textbf{\Centerstack{Individual class 1\\(n = 1730)}} & \textbf{\Centerstack{Individual class 2\\(n = 1772)}} & \textbf{\Centerstack{Individual class 3\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\

@@

		Total energy intake (kJ) & \Centerstack{7985.8\\(7823.3, 8146.295)} & \Centerstack{7341.8\\(7825.3, 8146.3)} & \Centerstack{7677.0\\(7555.8, 7799,8)} & < 0.001\\
		Carbohydrate percent\textsuperscript{\ddag} (\%) & 203.8 (199.8, 207.8) & 218.3 (212.9, 223.7) & 233.4 (229.6, 237.2) & < 0.001\\
		Carbohydrate percent (\%) & 40.6 (40.2, 41.0) & 47.3 (46.8, 47.8) & 48.3 (47.9, 48.6) & < 0.001\\

@@

		\multicolumn{5}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}\\
		\multicolumn{5}{l}{ BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.}\\
		\multicolumn{5}{l}{Variables from the blood tests (glucose and A1C) were weighted by blood sample weights, the others were}\\ 
		\multicolumn{5}{l}{weighted by nurse visiting weights.}\\

@@

		\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes}\\ 

>>>>

With two individual level latent classes \textbf{(Figure \ref{fig:CB2level2})}, one individual class is comprised of individuals with a relatively slightly higher proportion of having "low carbohydrate day" (22.1\%) compared to the other (17.4\%). This class represents nearly 65\% of the individuals. However, we believe these individual classes are not very distinguishable to each other.

@@

With three individual level latent classes \textbf{(Figure \ref{fig:level2})}, a low-carbohydrate eaters class, a moderate-carbohydrate eaters class, and a high-carbohydrate eaters class emerges. 43.1\% participants were identified as high-carbohydrate eaters, in these individuals, about 50\% of the days (2 out of 4 days) of their dietary diary were classified as having high carbohydrate days. Nearly 1 out of 4 days of their dietary diary were either "regular meals day" or "low carbohydrate day". 28.1\% participants fell into the low carbohydrate eaters class in the left hand side of \textbf{Figure \ref{fig:level2}}, their recordings of food intake showed that in more than 60\% of their days, they were having "regular meals" which was characterised as with highest amount of fat and alcohol consumptions as already described in \textbf{Table \ref{tab:day-level-features}}.

@@

The social-economic characteristics of the

@@

\caption{\label{tab:Level2tab1}Weighted means, percentages, and
95\% CIs of the social-economic characteristics by latent class memberships in the UK
adults. (NDNS RP 2008/09-2015/16, sample size = 6155)} \centering
\fontsize{9}{11}\selectfont

\begin{tabular}[t]{lcccc}
	\hiderowcolors
	\toprule
	\textbf{Variables} & \textbf{\Centerstack{Low carbo-\\hydrate eaters\\(n = 1730)}} & \textbf{\Centerstack{Moderate carbo-\\hydrate eaters\\(n = 1772)}} & \textbf{\Centerstack{High carbo\\hydrate eaters\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\
	\midrule
	\showrowcolors
	Total (\%) & 28.4 (26.9, 29.9) & 28.7 (27.1, 30.3) & 43.0 (41.3, 44.7) & \\
	Countries (\%) &  &  &  & 0.007\\
	\hspace{1em}England & 84.5 (81.7, 86.9) & 82.0 (79.3, 84.5) & 84.7 (82.3, 86.8) & \\
	\hspace{1em}Northern Ireland & 2.1 (1.6, 2.8) & 4.2 (3.2, 5.6) & 2.2 (1.7, 3.0) & \\
	\hspace{1em}Scotland & 9.1 (7.0, 11.8) & 8.6 (6.7, 11.1) & 8.0 (6.3, 10.2) & \\
	\hspace{1em}Wales & 4.3 (3.3, 5.6) & 5.1 (4.0, 6.4) & 5.1 (4.0, 6.4) & \\
	Age (years) & 51.0 (49.9, 52.1) & 40.3 (39.1, 41.6) & 51.7 (50.7, 52.7) & < 0.001\\
	Sex (\%) &  &  &  & 0.119\\
	\hspace{1em}Men & 50.0 (46.9, 53.1) & 50.2 (47.0, 53.5) & 46.6 (44.0, 49.1) & \\
	\hspace{1em}Women & 50.0 (46.9, 53.1) & 49.8 (46.5, 53.0) & 53.4 (50.9, 56.0) & \\
	Survey years (\% in rows) &  &  &  & 0.015\\
	\hspace{1em}1 & 32.5 (28.4, 36.9) & 26.3 (21.9, 31.2) & 41.2 (36.6, 46.0) & \\
	\hspace{1em}2 & 26.8 (22.6, 31.3) & 22.6 (18.6, 27.3) & 50.6 (45.8, 55.4) & \\
	\hspace{1em}3 & 22.6 (18.8, 26.9) & 33.7 (28.6, 39.2) & 43.6 (38.7, 48.7) & \\
	\hspace{1em}4 & 27.9 (24.1, 32.2) & 27.6 (23.8, 31.8) & 44.4 (40.2, 48.7) & \\
	\hspace{1em}5 & 27.9 (24.2, 32.0) & 28.7 (24.4, 33.5) & 43.3 (38.2, 48.6) & \\
	\hspace{1em}6 & 28.0 (24.0, 32.4) & 31.5 (26.9, 36.6) & 40.5 (35.8, 45.3) & \\
	\hspace{1em}7 & 29.1 (25.2, 33.4) & 29.0 (24.5, 34.0) & 41.8 (37.1, 46.7) & \\
	\hspace{1em}8 & 31.1 (27.3, 35.3) & 30.5 (25.9, 35.5) & 38.4 (34.1, 42.8) & \\
	Paid employment\textsuperscript{\dag} (\%) &  &  &  & 0.907\\
	\hspace{1em}Yes & 40.3 (37.0, 43.6) & 40.8 (37.1, 44.5) & 39.8 (37.1, 42.6) & \\
	\hspace{1em}No & 59.7 (56.4, 63.0) & 59.2 (55.5, 62.9) & 60.2 (57.4, 62.9) & \\
	Live with partner\textsuperscript{\ddag} (\%) &  &  &  & < 0.001\\
	\hspace{1em}Yes & 56.9 (53.6, 60.1) & 38.4 (35.2, 41.8) & 61.3 (58.7, 63.7) & \\
	\hspace{1em}No & 43.1 (39.9, 46.4) & 61.6 (58.2, 64.8)) & 38.7 (36.3, 41,3) & \\
	Household Income, \textsterling/year & \Centerstack{36558.5\\(34800.2, 38316.8)} & \Centerstack{27180.8\\(25597.9, 28763.7)} & \Centerstack{32171.6\\(31024.9, 33318.2)} & < 0.001\\
	Ethnicity (\%) &  &  &  & \\
	\hspace{1em}White & 94.2 (92.4, 95.6) & 79.5 (76.4, 82.3) & 91.9 (90.1, 93.4) & < 0.001\\
	\hspace{1em}Non-White & 5.8 (4.4, 7.6) & 20.5 (17.7, 23.6) & 8.1 (6.6, 9.9) & \\
	Education (\%) &  &  &  & \\
	\hspace{1em}Degree or higher & 29.0 (26.1, 32.1) & 23.3 (20.5, 26.3) & 26.2 (24.1, 28.5) & 0.019\\
	\hspace{1em}Lower than degree & 71.0 (67.9, 73.9) & 76.7 (73.7, 79.5) & 73.8 (71.5, 75.9) & \\
	\bottomrule
	\multicolumn{5}{l}{\textit{Note: }}\\
	\multicolumn{5}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling}\\
	\multicolumn{5}{l}{programme} \\
	\multicolumn{5}{l}{Variables were weighted by individual weights.}\\
	\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the \textit{F} test was used to determine differences between latent classes with}\\ 
	\multicolumn{5}{l}{Bonferroni correction to account for multiple testing across $>$ 2 classes. For categorical variables,}\\
	\multicolumn{5}{l}{ differences between latent classes were assessed using the adjusted Pearson $\chi^2$ test for survey data.} \\
	\multicolumn{5}{l}{\textsuperscript{\dag} Paid employment was defined as being in paid employment during the last 4 weeks prior to }\\
	\multicolumn{5}{l}{the survey.}\\
	\multicolumn{5}{l}{\textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally  } \\
	\multicolumn{5}{l}{recognised civil partnership.}\\
\end{tabular}

@@

	\textbf{Variables} & \textbf{\Centerstack{Low carbo-\\hydrate eaters\\(n = 1730)}} & \textbf{\Centerstack{Moderate carbo-\\hydrate eaters\\(n = 1772)}} & \textbf{\Centerstack{High carbo\\hydrate eaters\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\

@@

		Total energy intake (kJ) & \Centerstack{7985.8\\(7823.3, 8146.3)} & \Centerstack{7341.8\\(7825.3, 8146.3)} & \Centerstack{7677.0\\(7555.8, 7799.8)} & < 0.001\\
		Carbohydrate intake (g) & \Centerstack{203.8\\(199.8, 207.8)} & \Centerstack{218.3\\(212.9, 223.7)} & \Centerstack{233.4\\(229.6, 237.2)} & < 0.001\\
		Carbohydrate percent\textsuperscript{\ddag} (\%) & 40.6 (40.2, 41.0) & 47.3 (46.8, 47.8) & 48.3 (47.9, 48.6) & < 0.001\\

@@

		\multicolumn{5}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling }\\
		\multicolumn{5}{l}{programme; BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, }\\
		\multicolumn{5}{l}{diabetes mellitus.} \\
		\multicolumn{5}{l}{Variables from the blood tests (glucose and A1C) were weighted by blood sample weights,}\\ 
		\multicolumn{5}{l}{ the other variables were weighted by nurse visiting weights.}\\

@@

		\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the \textit{F} test was used to determine differences between latent classes}\\ 

### 2018-08-03 paper/Tables/2by2Table1.tex
tables figs of MLCA done, classes and bmi, dm, hyt estimates needed

\caption{\label{tab:tab2}Means, percentages, and 95 CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{lllll}
\hiderowcolors
\toprule
Variables & Individual class 1 (n = 1730) & Individual class (n = 1772) & Individual class 3 (n = 2653) & P value\textsuperscript{*}\\
\midrule
\showrowcolors
BMI (kg/m2) & 27.8 (27.4, 28.2) & 27.2 (26.7, 27.7) & 27.3 (26.9, 27.6) & 0.006\\
WC (cm) & 94.6 (93.5, 95.6) & 92.3 (91.0, 93.5) & 92.2 (91.4, 93.1) & 0.001\\
Smoking status (\%) &  &  &  & \\
\hspace{1em}Current & 20.4 (18.0, 23.0) & 27.8 (25.0, 30.9) & 17.1 (15.4, 19.0) & < 0.001\\
\hspace{1em}Ex-smoker & 29.3 (26.5, 32.2) & 16.8 (14.6, 19.2) & 26.1 (24.9, 28.3) & \\
\hspace{1em}Never & 50.3 (47.2, 32.2) & 55.4 (52.2, 58.6) & 56.8 (54.3, 59.3) & \\
Current drinking status (\%) &  &  &  & \\
\hspace{1em}Yes & 11.8 (10.0, 13.8) & 24.0 (21.2, 27.1) & 20.6 (18.7, 22.8) & < 0.001\\
Hypertension\textsuperscript{\dag} (\%) &  &  &  & \\
\hspace{1em}Yes & 33.4 (29.9, 37.1) & 21.1 (17.7, 24.9) & 31.2 (28.3, 34.2) & < 0.001\\
Total energy intake (kJ) & 7985.8 (7823.3, 8146.295) & 7341.8 (7825.3, 8146.3) & 7677 (7555.8, 7799,8) & < 0.001\\
Carbohydrate percent\textsuperscript{\ddag} (\%) & 203.8 (199.8, 207.8) & 218.3 (212.9, 223.7) & 233.4 (229.6, 237.2) & < 0.001\\
Carbohydrate percent (\%) & 40.6 (40.2, 41.0) & 47.3 (46.8, 47.8) & 48.3 (47.9, 48.6) & < 0.001\\
Protein intake (g) & 79.9 (77.9, 81.8) & 69.3 (67.6, 71.0) & 73.7 (72.5, 74.8) & < 0.001\\
Protein percent (\%) & 17.2 (16.9, 17.5) & 16.3 (16.0, 16.6) & 16.5 (16.3, 16.6) & < 0.001\\
Fat intake (g) & 74.7 (73.1, 76.4) & 63.8 (62.1, 65.5) & 65.7 (64.4, 67.0) & < 0.001\\
Fat percent (\%) & 35.4 (34.9, 35.8) & 32.5 (32.1, 32.9) & 32.0 (31.7, 32.3) & < 0.001\\
Glucose (mmol/l) & 5.20 (5.15, 5.26) & 5.09 (5.02, 5.17) & 5.13 (5.09, 5.12) & 0.051\\
A1C (\%) & 5.49 (5.45, 5.52) & 5.44 (5.40, 5.48) & 5.52 (5.49, 5.55) & 0.012\\
DM \textsuperscript{\S} & 6.9 (5.0, 9.3) & 3.5 (2.3, 5.3) & 4.1 (2.9, 5.6) & 0.011\\
Physical
activity (hours/day) \textsuperscript{\P} & 1.63 (1.43, 1.83) & 1.32 (1.15, 1.49) & 1.65 (1.49, 1.81) & 0.016\\
\bottomrule
\multicolumn{5}{l}{\textit{Note: }}\\
\multicolumn{5}{l}{Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}\\
\multicolumn{5}{l}{ BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.}\\
\multicolumn{5}{l}{Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.}\\
\multicolumn{5}{l}{Glucose and A1C levels are estimated in subgroups of people without diabetes.}\\
\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes with Bonferroni correction to account}\\
\multicolumn{5}{l}{for multiple testing across >2 classes. For categorical variables, differences between latent classes were assessed using the adjusted}\\
\multicolumn{5}{l}{Pearson Chi-2 test for survey data.}\\
\multicolumn{5}{l}{\textsuperscript{\dag} Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for}\\
\multicolumn{5}{l}{hypertension.}\\
\multicolumn{5}{l}{\textsuperscript{\ddag} Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake}\\
\multicolumn{5}{l}{\textsuperscript{\S} DM was defined by A1C > 6.5\%.}\\
\multicolumn{5}{l}{\textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and}\\
\multicolumn{5}{l}{recreational activities during the survey.}\\
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:tab2}Means, percentages, and 95 CIs of the characteristics by latent class memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{lllll}
\hiderowcolors
\toprule
Variables & Individual class 1 (n = 1730) & Individual class (n = 1772) & Individual class 3 (n = 2653) & P value\textsuperscript{*}\\
\midrule
\showrowcolors
BMI (kg/m2) & 27.8 (27.4, 28.2) & 27.2 (26.7, 27.7) & 27.3 (26.9, 27.6) & 0.006\\
WC (cm) & 94.6 (93.5, 95.6) & 92.3 (91.0, 93.5) & 92.2 (91.4, 93.1) & 0.001\\
Smoking status (\%) &  &  &  & \\
\hspace{1em}Current & 20.4 (18.0, 23.0) & 27.8 (25.0, 30.9) & 17.1 (15.4, 19.0) & < 0.001\\
\hspace{1em}Ex-smoker & 29.3 (26.5, 32.2) & 16.8 (14.6, 19.2) & 26.1 (24.9, 28.3) & \\
\hspace{1em}Never & 50.3 (47.2, 32.2) & 55.4 (52.2, 58.6) & 56.8 (54.3, 59.3) & \\
Current drinking status (\%) &  &  &  & \\
\hspace{1em}Yes & 11.8 (10.0, 13.8) & 24.0 (21.2, 27.1) & 20.6 (18.7, 22.8) & < 0.001\\
Hypertension\textsuperscript{\dag} (\%) &  &  &  & \\
\hspace{1em}Yes & 33.4 (29.9, 37.1) & 21.1 (17.7, 24.9) & 31.2 (28.3, 34.2) & < 0.001\\
Total energy intake (kJ) & 7985.8 (7823.3, 8146.295) & 7341.8 (7825.3, 8146.3) & 7677 (7555.8, 7799,8) & < 0.001\\
Carbohydrate intake (g) & 203.8 (199.8, 207.8) & 218.3 (212.9, 223.7) & 233.4 (229.6, 237.2) & < 0.001\\
Carbohydrate percent\textsuperscript{\ddag} (\%) & 40.6 (40.2, 41.0) & 47.3 (46.8, 47.8) & 48.3 (47.9, 48.6) & < 0.001\\
Protein intake (g) & 79.9 (77.9, 81.8) & 69.3 (67.6, 71.0) & 73.7 (72.5, 74.8) & < 0.001\\
Protein percent (\%) & 17.2 (16.9, 17.5) & 16.3 (16.0, 16.6) & 16.5 (16.3, 16.6) & < 0.001\\
Fat intake (g) & 74.7 (73.1, 76.4) & 63.8 (62.1, 65.5) & 65.7 (64.4, 67.0) & < 0.001\\
Fat percent (\%) & 35.4 (34.9, 35.8) & 32.5 (32.1, 32.9) & 32.0 (31.7, 32.3) & < 0.001\\
Glucose (mmol/l) & 5.20 (5.15, 5.26) & 5.09 (5.02, 5.17) & 5.13 (5.09, 5.12) & 0.051\\
A1C (\%) & 5.49 (5.45, 5.52) & 5.44 (5.40, 5.48) & 5.52 (5.49, 5.55) & 0.012\\
DM \textsuperscript{\S} & 6.9 (5.0, 9.3) & 3.5 (2.3, 5.3) & 4.1 (2.9, 5.6) & 0.011\\
Physical
activity (hours/day) \textsuperscript{\P} & 1.63 (1.43, 1.83) & 1.32 (1.15, 1.49) & 1.65 (1.49, 1.81) & 0.016\\
\bottomrule
\multicolumn{5}{l}{\textit{Note: }}\\
\multicolumn{5}{l}{Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}\\
\multicolumn{5}{l}{ BMI body mass index; WC, waist circumference; A1C, haemoglobin A1c; DM, diabetes mellitus.}\\
\multicolumn{5}{l}{Variables from the blood tests (glucose and A1C) are weighted by blood sample weights, the others are weighted by individual weights.}\\
\multicolumn{5}{l}{Glucose and A1C levels are estimated in subgroups of people without diabetes.}\\
\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes with Bonferroni correction to account}\\
\multicolumn{5}{l}{for multiple testing across >2 classes. For categorical variables, differences between latent classes were assessed using the adjusted}\\
\multicolumn{5}{l}{Pearson Chi-2 test for survey data.}\\
\multicolumn{5}{l}{\textsuperscript{\dag} Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for}\\
\multicolumn{5}{l}{hypertension.}\\
\multicolumn{5}{l}{\textsuperscript{\ddag} Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake}\\
\multicolumn{5}{l}{\textsuperscript{\S} DM was defined by A1C > 6.5\%.}\\
\multicolumn{5}{l}{\textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and}\\
\multicolumn{5}{l}{recreational activities during the survey.}\\
\end{tabular}
\end{table}
